19Q2

### 2020-01-04 19Q2.Rmd

g2p_prot <- unique(filter(g2p_mut, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
g2p_prot$Drug_Gene_Protein_Change_Lineage <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
g2p_prot$Gene_Protein_Change_Lineage <- with(g2p_prot, ifelse(is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Gene_Protein_Change, "_", disease)))

@@

crispr_prot <- merge(crispr_melt, grid, by = c("DepMap_ID", "Gene"), all = TRUE)
crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene", "Gene_Protein_Change"), all = TRUE)  %>% drop_na(Score)
crispr_prot <- merge(crispr_prot, ccl_meta, by = "DepMap_ID", all.x = TRUE)
crispr_prot$Change_Status <- ifelse(is.na(crispr_prot$Change_Status), "No", crispr_prot$Change_Status)
crispr_prot$Drug <- "CRISPR"
crispr_prot$Gene_Protein_Change_Lineage <- with(crispr_prot, ifelse(is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Gene_Protein_Change, "_", disease)))
crispr_prot$Drug_Gene_Protein_Change <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
crispr_prot$Drug_Gene_Protein_Change_Lineage <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
crispr_prot$G2P_Drug_Gene_Protein_Change <- "No"
crispr_prot$G2P_Protein_Change <- ifelse(crispr_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
crispr_prot$G2P_Drug_Gene_Protein_Change_Lineage <- "No"
crispr_prot <- merge(crispr_prot, unique(select(g2p_prot, Gene_Protein_Change, Direction_Curated)), by = "Gene_Protein_Change", all.x = TRUE)
crispr_prot$Database <- "CRISPR"

saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes_20191223.rds", compress = "xz")
```

```{r, eval = TRUE}
crispr_fus <- readRDS("./data_munging/19Q2/crispr_fusions.rds")
# crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes_20191223.rds")
```

@@

@@

gene_prots <- union(union(unique(ccle_signif_prot$Gene_Protein_Change), union(unique(ctrp_signif_prot$Gene_Protein_Change), unique(gdsc_signif_prot$Gene_Protein_Change))), unique(crispr_signif_prot$Gene_Protein_Change))

# all_directions <- unique(rbind(select(crispr_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ccle_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ctrp_prot, Gene_Protein_Change, Drug, Direction_Curated), select(gdsc_prot, Gene_Protein_Change, Drug, Direction_Curated)))
# all_directions <- filter(all_directions, !is.na(Direction_Curated))
# saveRDS(all_directions, "./data_munging/rds/protein_changes_directions.rds")
all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")

crispr_signif_prot_4plot <- merge(merge(merge(crispr_signif_prot, unique(select(crispr_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(crispr_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
ctrp_signif_prot_4plot <- merge(merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
gdsc_signif_prot_4plot <- merge(merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)

@@

all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
crispr_signif_prot_lin <- readRDS("./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
crispr_signif_prot_lin <- merge(crispr_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
ccle_signif_prot_lin <- readRDS("./data_munging/rds/ccle_signif_protein_changes_lineage.rds")
ccle_signif_prot_lin <- merge(ccle_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
ctrp_signif_prot_lin <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_lineage.rds")
ctrp_signif_prot_lin <- merge(ctrp_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
gdsc_signif_prot_lin <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
gdsc_signif_prot_lin <- merge(gdsc_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)

@@

## Figure 2: G2P summary heatmap

@@

png(filename = "./plots/manuscript/figure2_g2p_summary_heatmap.png", width = 10, height = 9, units = "in", res = 500)
draw(hta + ht, gap = unit(5, "mm"), heatmap_legend_side = "top")
dev.off()
```

## Figure 3: Mutation status

>>>>

g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
g2p_prot$Drug_Gene_Protein_Change_Lineage <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
g2p_prot$Gene_Protein_Change_Lineage <- with(g2p_prot, ifelse(is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Gene_Protein_Change, "_", disease)))

@@

crispr_prot <- merge(crispr_melt, grid, by = c("DepMap_ID", "Gene"), all = TRUE)
crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene", "Gene_Protein_Change"), all = TRUE)  %>% drop_na(Score)
crispr_prot <- merge(crispr_prot, ccl_meta, by = "DepMap_ID", all.x = TRUE)
crispr_prot$Change_Status <- ifelse(is.na(crispr_prot$Change_Status), "No", crispr_prot$Change_Status)
crispr_prot$Drug <- "CRISPR"
crispr_prot$Gene_Protein_Change_Lineage <- with(crispr_prot, ifelse(is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Gene_Protein_Change, "_", disease)))
crispr_prot$Drug_Gene_Protein_Change <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
crispr_prot$Drug_Gene_Protein_Change_Lineage <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))

crispr_prot$Database <- "CRISPR"

saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes_20200103.rds", compress = "xz")
```

```{r, eval = TRUE}
crispr_fus <- readRDS("./data_munging/19Q2/crispr_fusions.rds")
# crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes_20200103.rds")
```

@@

```{r}
dataframe = crispr_prot
grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change")
g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change[!is.na(g2p_prot$Gene_Protein_Change)]))
outfile = "./data_munging/rds/crispr_signif_protein_changes.rds"

    count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status)
    count_n_wide <- dcast(count_n, Drug_Gene_Protein_Change ~ Change_Status, value.var = "n", fill = 0) %>% separate(Drug_Gene_Protein_Change, sep = "_", c("Drug", "Gene_Protein_Change"), extra = "merge", remove = FALSE)
    colnames(count_n_wide) <- c("Drug_Gene_Protein_Change", "Drug", "Gene_Protein_Change", "Change_Status_0_count", "Change_Status_1_count")
    count_n_filt <- filter(count_n, n >= 3)
    count_category <- count_n_filt %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
    dg_keep <- intersect(count_n_filt$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% dg_keep)
    dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
    signif$`n WT/mut` <- with(signif, paste0(Change_Status_0_count, "/", Change_Status_1_count))
    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No") }
    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Gene_Protein_Change %in% g2p_list, "Yes", "No")  }
```

@@

gene_prots <- union(union(union(unique(ccle_signif_prot$Gene_Protein_Change), unique(ctrp_signif_prot$Gene_Protein_Change)), unique(gdsc_signif_prot$Gene_Protein_Change)), unique(crispr_signif_prot$Gene_Protein_Change))

crispr_directions <- unique(select(g2p_prot, Gene_Protein_Change, Direction_Curated) %>% drop_na(Direction_Curated))
crispr_directions_n <- crispr_directions %>% count(Gene_Protein_Change)
crispr_directions <- merge(crispr_directions, crispr_directions_n, by = "Gene_Protein_Change", all = TRUE)
crispr_directions$Direction_Curated <- with(crispr_directions, ifelse(n == 2, "both", Direction_Curated))
crispr_directions <- unique(crispr_directions %>% select(-n))

crispr_signif_prot_4plot <- merge(merge(merge(crispr_signif_prot, unique(select(crispr_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(crispr_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), crispr_directions, by = "Gene_Protein_Change", all.x = TRUE)
ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), unique(select(g2p_prot, Drug, Gene_Protein_Change, Direction_Curated)),  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
ctrp_signif_prot_4plot <- merge(merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), unique(select(g2p_prot, Drug, Gene_Protein_Change, Direction_Curated)),  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
gdsc_signif_prot_4plot <- merge(merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), unique(select(g2p_prot, Drug, Gene_Protein_Change, Direction_Curated)),  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)

@@

crispr_directions <- unique(select(g2p_prot, Gene_Protein_Change_Lineage, Direction_Curated) %>% drop_na(Direction_Curated))
crispr_directions_n <- crispr_directions %>% count(Gene_Protein_Change_Lineage)
crispr_directions <- merge(crispr_directions, crispr_directions_n, by = "Gene_Protein_Change_Lineage", all = TRUE)
crispr_directions$Direction_Curated <- with(crispr_directions, ifelse(n == 2, "both", Direction_Curated))
crispr_directions <- unique(crispr_directions %>% select(-n))
crispr_signif_prot_lin <- readRDS("./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
crispr_signif_prot_lin <- merge(crispr_signif_prot_lin, crispr_directions, by = "Gene_Protein_Change_Lineage", all.x = TRUE)

ccle_signif_prot_lin <- readRDS("./data_munging/rds/ccle_signif_protein_changes_lineage.rds")
ccle_signif_prot_lin <- merge(ccle_signif_prot_lin, unique(select(g2p_prot, Drug, Gene_Protein_Change, Drug_Gene_Protein_Change_Lineage, Direction_Curated)), by = c("Drug_Gene_Protein_Change_Lineage", "Gene_Protein_Change", "Drug"), all.x = TRUE)

ctrp_signif_prot_lin <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_lineage.rds")
ctrp_signif_prot_lin <- merge(ctrp_signif_prot_lin, unique(select(g2p_prot, Drug, Gene_Protein_Change, Drug_Gene_Protein_Change_Lineage, Direction_Curated)), by = c("Drug_Gene_Protein_Change_Lineage", "Gene_Protein_Change", "Drug"), all.x = TRUE)

gdsc_signif_prot_lin <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
gdsc_signif_prot_lin <- merge(gdsc_signif_prot_lin, unique(select(g2p_prot, Drug, Gene_Protein_Change, Drug_Gene_Protein_Change_Lineage, Direction_Curated)), by = c("Drug_Gene_Protein_Change_Lineage", "Gene_Protein_Change", "Drug"), all.x = TRUE)

@@

## Data summaries

```{r Supp2}
# How many datasets each drug was screened in
hta_data <- data.frame(Drug = rownames(g2p_dg_counts), CCLE = NA, CTRP = NA, GDSC = NA)
hta_data$CCLE <- ifelse(hta_data$Drug %in% unique(ccle$Drug), 1, 0)
hta_data$CTRP <- ifelse(hta_data$Drug %in% unique(ctrp$Drug), 1, 0)
hta_data$GDSC <- ifelse(hta_data$Drug %in% unique(gdsc$Drug), 1, 0)
rownames(hta_data) <- hta_data$Drug
hta_data$Drug <- NULL
hta_data$NumDatasetsScreened <- rowSums(hta_data)

ggplot(data = g2p) +
  geom_bar(mapping = aes(x = disease))

# How many G2P indications are for each disease
g2p_munge <- select(g2p, disease)
g2p_munge <- g2p_munge %>% count(disease)
g2p_munge$Perc <- g2p_munge$n / sum(g2p_munge$n) * 100
g2p_munge <- g2p_munge[order(g2p_munge$Perc),]
g2p_munge$disease <- factor(g2p_munge$disease, levels = g2p_munge$disease)
ggplot(data = g2p_munge) +
  geom_bar(mapping = aes(x = disease, y = Perc), stat = "identity") +
  geom_text(aes(x = disease, y = Perc + 3, label = round(Perc, 1))) +
  scale_y_continuous(breaks = seq(0, 100, by = 10), labels = seq(0, 100, by = 10)) +
  coord_flip()
```

```{r eval=FALSE}
ccle_ccls <- unique(ccle$DepMap_ID)
ctrp_ccls <- unique(ctrp$DepMap_ID)
gdsc_ccls <- unique(gdsc$DepMap_ID)
crispr_ccls <- unique(crispr$DepMap_ID)
# overlap <- calculate.overlap(x = list("CCLE" = ccle_ccls, "CTRP" = ctrp_ccls, "GDSC" = gdsc_ccls, "CRISPR" = crispr_ccls))

ccl_filter <- filter(ccl_meta, DepMap_ID %in% Reduce(intersect, list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls)))

futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
ccl_venn <- venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls),
             filename = NULL,
             height = 2000, width = 2000, resolution = 500,
             lwd = 1, cex = 1,
             category.names = c("CCLE", "CTRP", "GDSC", "CRISPR"),
             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
             # cat.dist = c(0.06, 0.06, 0.035),
             fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))

ccle_drugs <- unique(ccle$Drug)
ctrp_drugs <- unique(ctrp$Drug)
gdsc_drugs <- unique(gdsc$Drug)

futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
drug_venn <- venn.diagram(x = list(ccle_drugs, ctrp_drugs, gdsc_drugs),
             filename = NULL,
             height = 2000, width = 2000, resolution = 500,
             lwd = 1, cex = 1.4,
             category.names = c("CCLE", "CTRP", "GDSC"),
             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
             cat.dist = c(0.06, 0.06, 0.035),
             fill = c("palegreen3", "slategray3", "paleturquoise3"))
```

```{r Supp1_summary, fig.height=7, fig.width=20, warning=FALSE, eval=FALSE}
maf_g2p <- filter(maf_df, Gene %in% g2p_gene_order) %>% merge(ccl_meta, by = "DepMap_ID")
maf_g2p <- with(maf_g2p, maf_g2p[order(disease),])
maf_g2p_wide <- dcast(data = maf_g2p, formula = Gene ~ DepMap_ID, value.var = "Mutation", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
maf_g2p_wide <- ifelse(maf_g2p_wide == 1, "Mutant", "Wildtype")
maf_g2p_annot_df <- unique(select(maf_g2p, DepMap_ID, disease)) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID) %>% `colnames<-`("Lineage")

# Cell line/mutation heatmap
maf_g2p_annot <- HeatmapAnnotation(df = maf_g2p_annot_df, annotation_name_side = "left", annotation_legend_param = list(Lineage = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 12), title_position = "topleft", nrow = 5)))

maf_g2p_legend_list <- list(title = "Mutation status", legend_direction = "horizontal", border = "gray70", nrow = 1, title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 12))

maf_g2p_ht <- Heatmap(maf_g2p_wide,
                      col = c("Mutant" = "black", "Wildtype" = "white"),
                      rect_gp = gpar(col = "white"),
                      heatmap_legend_param = maf_g2p_legend_list,
                      cluster_rows = FALSE, 
                      cluster_columns = TRUE, 
                      row_names_side = "left",
                      row_names_gp = gpar(fontsize = 10),
                      show_column_names = FALSE,
                      row_title = "Genes",
                      row_title_gp = gpar(fontface = "bold", fontsize = 20),
                      column_title = "Cell lines", 
                      column_title_gp = gpar(fontface = "bold", fontsize = 20),
                      column_title_side = "top",
                      top_annotation = maf_g2p_annot)

draw(maf_g2p_ht, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_side = "top")
```

```{r supp_stats, eval=FALSE}
maf_g2p_summ_gene <- maf_g2p %>% group_by(Gene) %>% count(Mutation) %>% filter (Mutation == 1) %>% merge(unique(select(maf_g2p, DepMap_ID, Gene)) %>% count(Gene), by = "Gene", suffixes = c("_mut", "_cell_lines"), all = TRUE)
maf_g2p_summ_gene$PercCellLinesMutated <- maf_g2p_summ_gene$n_mut/maf_g2p_summ_gene$n_cell_lines * 100

maf_g2p_summ <- maf_g2p %>% group_by(disease) %>% count(Mutation) %>% filter (Mutation == 1) %>% merge(unique(select(maf_g2p, DepMap_ID, disease)) %>% count(disease), by = "disease", suffixes = c("_mut", "_cell_lines"), all = TRUE)
maf_g2p_summ$MutPerCCL <- maf_g2p_summ$n_mut/maf_g2p_summ$n_cell_lines

sum(maf_g2p_summ$n_cell_lines)
777/1588
sum(maf_g2p_summ$n_mut[!is.na(maf_g2p_summ$n_mut)])
2067/3151
```

@@

png(filename = "./plots/manuscript_final/g2p_summary_heatmap.png", width = 10, height = 9, units = "in", res = 500)
draw(hta + ht, gap = unit(5, "mm"), heatmap_legend_side = "top")
dev.off()
```

```{r fig.height=8, fig.width=15, eval=FALSE}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top"))

crispr_signif_g2p_dg_summ <- filter(crispr_signif_g2p_g, InG2P == "Yes") 
ccle_signif_g2p_dg_summ <- filter(ccle_signif_g2p_dg, InG2P == "Yes") 
ctrp_signif_g2p_dg_summ <- filter(ctrp_signif_g2p_dg, InG2P == "Yes") 
gdsc_signif_g2p_dg_summ <- filter(gdsc_signif_g2p_dg, InG2P == "Yes")

crispr_mut_filt <- filter(crispr, Gene %in% filter(crispr_signif_g2p_dg_summ, p < 0.05)$Gene)
crispr_mut_filt_plot <- ggplot(data = crispr_mut_filt, aes(x = as.character(Mutation), y = Score) )+
  facet_wrap(~ Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "CRISPR", x = "Mutation Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

ccle_mut_filt <- filter(ccle, Drug_Gene %in% filter(ccle_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "CCLE", x = "Mutation Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

ctrp_mut_filt <- filter(ctrp, Drug_Gene %in% filter(ctrp_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
ctrp_mut_filt_plot <- ggplot(data = ctrp_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 7) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07,) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "CTRP", x = "Mutation Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

gdsc_mut_filt <- filter(gdsc, Drug_Gene %in% filter(gdsc_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
gdsc_mut_filt_plot <- ggplot(data = gdsc_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07, ) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "turquoise4", "0" = "paleturquoise3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
  labs(title = "GDSC", x = "Mutation Status") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

lay <- rbind(c(1, 1, 1, 1, 1),
             c(1, 1, 1, 1, 1),
             c(1, 1, 1, 1, 1),
             c(2, 2, 2, 2, 2),
             c(3, 3, 5, 5, 5),
             c(4, 4, 4, 4, 4))

png(filename = "./plots/manuscript_final/all_mutation_agnostic_boxplots.png", width = 15, height = 15, units = "in", res = 500)
grid.arrange(layout_matrix = lay,
             arrangeGrob(ht_mut_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(crispr_mut_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ccle_mut_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ctrp_mut_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(gdsc_mut_filt_plot), left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
dev.off()
```

```{r prot_changes, eval = FALSE, fig.height=15, fig.width=15}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.009)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
ht_prot_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top"))

crispr_signif_prot_summ <- filter(crispr_signif_prot, InG2P == "Yes") 
ccle_signif_prot_summ <- filter(ccle_signif_prot, InG2P == "Yes") 
ctrp_signif_prot_summ <- filter(ctrp_signif_prot, InG2P == "Yes") 
gdsc_signif_prot_summ <- filter(gdsc_signif_prot, InG2P == "Yes")
